Universal Anonymous Signatures

### 2022-10-03 prism-backend/research/gsac/relationships.tex
Forgot to update theorems. Need to sync with proofs.
Pass.

In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
models of related schemes in the literature.
Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
that they securely instantiate the models for the presented schemes, if the
corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
we rely on the functions described in \figref{fig:func-restrictions}. Observe
that all the \fissue functions listed in \figref{fig:func-restrictions} are
\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
\UAS-acceptable if $F$ is a secure PRF \cite{kl14}.

@@

We adopt the model in \cite{bsz05}. In this abstraction of group signatures, the
opener returns an index uniquely identifying the group member that created a
signature, along with a correctness proof. For ease of exposition, assume that,
w.l.o.g., this index is just the public key that the group member generates
randomly when joining the group\footnote{The user public key is assumed to be
  accessible from a public table in \cite{bsz05}, so it is easy to translate the
  public key into an index, if needed.}. A group signature scheme, according to
\cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
\Judge algorithms, as well as an $\langle\Obtain,\Issue\rangle$ interactive
protocol. Their intuition is similar to that of \UAS, so we refer to
\cite{bsz05} for detailed descriptions. For ease of reference, we replicate the
security games in \figref{fig:model-gs}.

@@

      \vspace*{5em}

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}_{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg)
      }       
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}_{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcreturn \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}_{anon} \gets \lbrace \oracle{Ch},\oracle{Open},\oracle{SndToU},
    \oracle{WReg},\oracle{USK},\oracle{CrptU} \rbrace$,
    $\mathcal{O}_{trace} \gets \lbrace \oracle{SndToI},\oracle{AddU},
    \oracle{RReg},\oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$,
    and $\mathcal{O}_{frame} \gets \lbrace \oracle{SndToU},\oracle{WReg},
    \oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $F$ is a
PRF. In that case, its output is a random-looking string that depends on the
user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
will be the same per $(\upk,I)$ pair, and can be used by issuer $I$ to prevent
issuing more than one credential per user. Basically, the issuer maintains a
list of received $\yissue = F(\upk,I)$ values, and rejects issuing a credential
for already existing ones. From this, the GS algorithms are as
follows:

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and one instance of \KeyGen and \ISet with $\fissue^{single,H,I}$ (both for
  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Upon receiving
  the \yissue value, the issuer checks if it already exists in a list $L$
  (initially set to $\emptyset$); if it exists, aborts issuance. Otherwise, it
  completes the protocol and adds $\yissue$ to $L$. It is responsibility of the
  issuer to maintain $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{SIGN}}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{\oracle{SIGN},\oracle{CORR}}
        (\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{SIGN}$
    oracle accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a
    list of queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$.
    $\oracle{CORR}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
    added to $CU$.}
  \label{fig:model-rs}  
\end{figure}

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGenHideIss.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. For each of
  the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
  and $\ipk_i \gets \ISet((\upk_i,\usk_i),\fissue^{\sring})$, where $\sring =
  \lbrace \upk_i \rbrace_{i\in[n]}$. Run also $(\opk,\osk) \gets \OKeyGen(\parm,
  \finsp^0)$. Set $\pk_i \gets (\ipk_i,\opk)$ and $\sk_i \gets \usk_i$, for
  $i\in[n]$.
\item[$\Sig \gets \Sign(\sk_i,R,\msg).$]
  The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
  [n]$ where $\pk_i \in R$, first acts both as user and issuer to self-issue a
  credential \Cred over an attribute set \attrs such that $\attrs \subseteq
  \sring$. The user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$,
  and computes the ring signature by running $\Sig = (\sig,\yeval) \gets
  \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
  \CUASGenHideIss. Note that \dattrs defines the public keys within
  $\attrs \subseteq \sring$ to be revealed through \yeval.
\item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
  runs $\Verify(\opk,\yeval,\Sig,\msg,\feval^{\sring,\dattrs})$ as in
  \CUASGenHideIss. Note that, in valid signatures, $\yeval = \lbrace
  \ipk_i\rbrace_{i\in\dattrs}$.
\end{description}

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure, which restricts to one credential per presentation. Therein, an
anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
$IssKeyGen$), and $UserKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols. We
refer to \cite{fhs19} for the full details. For ease of reference, we summarize
the security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

\begin{description}
% \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
%   \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
%   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From \CUASGenInt, run $\parm'
  \gets \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
  \finsp^0)$, and set $\parm \gets (\parm',\opk)$. Run $(\upk,\usk) \gets
  \KeyGen(\parm')$ and $\ipk \gets \ISet(\upk,\usk,\fissue^1)$. Set $\isk \gets
  \usk$.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs $\langle \Obtain,\Issue \rangle$ from \CUASGenInt.
\item[$\langle 1/0,((\yeval,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle \Sign, \Verify\rangle$ of  \CUASGenInt,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key. The \yeval value
  output by the verifier, when it accepts, is the $\yeval^0$ value produced by
  \Sign in \CUASGenInt.
\end{description}

>>>>

In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
models of related schemes in the literature.
Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
that they securely instantiate the models for the presented schemes, if the
corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
we rely on the functions described in \figref{fig:func-restrictions}. Observe
that all the \fissue functions listed in \figref{fig:func-restrictions} are
\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
\UAS-acceptable if $H$ is a secure PRF \cite{kl14}.

@@

We adopt the model in \cite{bsz05}. In this abstraction of group signatures, the
opener returns an index uniquely identifying the group member that created a
signature, along with a correctness proof. For ease of exposition, assume that,
without loss of generality, this index is just the public key that the group
member generates randomly when joining the group\footnote{The user public key is
  assumed to be
  accessible from a public table in \cite{bsz05}, so it is easy to translate the
  public key into an index, if needed.}. A group signature scheme, according to
\cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
\Judge algorithms, as well as an $\langle\Obtain,\Issue\rangle$ interactive
protocol. Their intuition is similar to that of \UAS, so we refer to
\cite{bsz05} for detailed descriptions. For ease of reference, we replicate the
security games in \figref{fig:model-gs}.

@@

      \vspace*{3em}

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}_{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg)
      }       
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}_{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcreturn \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to ease comparison with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}_{anon} \gets \lbrace \oracle{Ch},\oracle{Open},\oracle{SndToU},
    \oracle{WReg},\oracle{USK},\oracle{CrptU} \rbrace$,
    $\mathcal{O}_{trace} \gets \lbrace \oracle{SndToI},\oracle{AddU},
    \oracle{RReg},\oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$,
    and $\mathcal{O}_{frame} \gets \lbrace \oracle{SndToU},\oracle{WReg},
    \oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $H$ is a
PRF. In that case, its output is a random-looking string that depends on the
user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
will be the same per $(I,\upk)$ pair, and can be used by issuer $I$ to prevent
issuing more than one credential per user. Basically, the issuer maintains a
list of received $\yissue = H(I,\upk)$ values, and rejects issuing a credential
for already existing ones. From this, the GS algorithms are as
follows:

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and two instances of \KeyGen. One followed by \ISet with $\fissue^{single,H,
    I}$ for the same user, who will be the issuer; and another for a different
  user, who will be the opener, followed with \OKeyGen with $\finsp^{\upk}$.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Upon receiving
  the \yissue value, the issuer checks if it already exists in a list $L$
  (initially set to $\emptyset$); if it exists, aborts issuance. Otherwise, it
  completes the protocol and adds $\yissue$ to $L$. It is responsibility of the
  issuer to maintain $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$, which internally runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{Sign}}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{\oracle{Sign},\oracle{Corr}}
        (\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~\oracle{Sign}(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{Sign}$
    oracle accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a
    list of queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$.
    $\oracle{Corr}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
    added to $CU$.}
  \label{fig:model-rs}  
\end{figure}

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGenHideIss.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. For each of
  the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
  and $\ipk_i \gets \ISet((\upk_i,\usk_i),\fissue^{\sring})$, where $\sring =
  \lbrace \upk_i \rbrace_{i\in[n]}$. Run also $(\opk,\osk) \gets \OKeyGen(\parm,
  \finsp^0)$. Set $\pk_i \gets (\ipk_i,\opk)$ and $\sk_i \gets \usk_i$, for
  $i\in[n]$.
\item[$\Sig \gets \Sign(\sk_i,R,\msg).$]
  The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
  [n]$ where $\pk_i \in R$, first acts both as user and issuer to self-issue a
  credential \Cred over an attribute set \attrs such that $\attrs = \sring$. The
  user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$, and computes
  the ring signature by running $\Sig = (\sig,\yeval) \gets
  \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
  \CUASGenHideIss. Note that \dattrs defines the public keys within
  $\attrs = \sring$ to be revealed through \yeval.
\item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
  runs $\Verify(\opk,\yeval,\Sig,\msg,\feval^{\sring,\dattrs})$ as in
  \CUASGenHideIss. Note that, in valid signatures, $\yeval = \lbrace
  \ipk_i\rbrace_{i\in\dattrs}$.
\end{description}

@@

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure, which restricts to one credential per presentation. Therein, an
anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
$IssKeyGen$), and $UserKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols. We
refer to \cite{fhs19} for the full details. For ease of reference, we give
the security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

\begin{description}
% \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
%   \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
%   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From \CUASGenInt, run $\parm'
  \gets \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
  \finsp^0)$, and set $\parm \gets (\parm',\opk)$. Run $(\upk,\usk) \gets
  \KeyGen(\parm')$ and $\ipk \gets \ISet(\upk,\usk,\fissue^1)$. Set $\isk \gets
  \usk$.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs $\langle \Obtain,\Issue \rangle$ from \CUASGenInt.
\item[$\langle 1/0,((\yeval,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle \Sign, \Verify\rangle$ of  \CUASGenInt,
  using $\feval^{\dattrs}$ as evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key. The \yeval value
  output by \Verify, when it accepts, is the $\yeval^0$ value output by
  \Sign in \CUASGenInt.
\end{description}

### 2022-10-03 prism-backend/research/gsac/uas-paper.tex
Pass.

  In this work, we make a further effort in order to come up with a flexible
  game-based model that generalises and unifies GS and AC schemes. The key to
  this flexibility lies in functional placeholders
  that, with careful constraints, still allow to capture generalised notions of
  the usual anonymity, unforgeability and non-frameability properties. We refer
  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).

  To showcase the generality of \UAS, we give a construction following our
  model and prove that, from it, we can easily build multiple
  variants of group signatures, anonymous credentials, and ring signatures, just
  by giving concrete definitions of the mentioned functional placeholders.

  Our main theoretical contribution is unifying previously separate (albeit
  close) systems under the same generalised model. Such unified model also
  allows to, very easily, build ``hybrid'' systems combining features
  of previously separately modelled constructions: e.g., anonymous credentials
  with conditional deanonymization based on their attributes.

  In practice, this means that cryptographic engineers and system designers
  can reach the desired utility-vs-privacy tradeoff that best suits their needs,
  just by defining a few functions -- but without needing to prove security from
  scratch or implement a whole system.
\end{abstract}

>>>>

  In this work, we make a further effort in order to come up with a flexible
  game-based model that generalises and unifies GS and AC schemes. The key to
  this flexibility lies in functional placeholders that, with careful
  constraints, allow to capture generalised notions of the usual anonymity,
  unforgeability and non-frameability properties. We refer to this unified model
  as \emph{Universal Anonymous Signatures} (\UAS).

  To showcase the generality of \UAS, we give a construction following our model
  and prove that, from it, we can easily build multiple variants of group
  signatures, anonymous credentials, and even ring signatures, just by giving
  concrete definitions of the mentioned functional placeholders.

  Our main theoretical contribution is thus unifying previously separate (albeit
  close) systems under the same generalised model. Such unified model also
  allows to, very easily, build ``hybrid'' systems combining features of its
  ancestors: e.g., anonymous credentials with conditional deanonymization based
  on their attributes.

  In practice, this means that cryptographic engineers and system designers
  can reach the desired utility-vs-privacy tradeoff that best suits their needs,
  just by defining a few functions -- but without needing to model and prove
  security from scratch or implement a whole system.
\end{abstract}
